---
title: "Dev Data Products W4 Pitch"
author: "Ryan Summe"
date: "2024-05-18"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
```

# DDP: Week 4 Project

Shiny Web App + Slides
Storms!

## Data Set

My [shiny app](https://raesu.shinyapps.io/ddpw4/) is based on `storms`, a data set from `dplyr`. From the documentation: 

"This dataset is the NOAA Atlantic hurricane database best track data, https://www.nhc.noaa.gov/data/#hurdat. The data includes the positions and attributes of storms from 1975-2022. Storms from 1979 onward are measured every six hours during the lifetime of the storm. Storms in earlier years have some missing data.'

## Storms Dataset Preview

```{r}
storms |> glimpse()
```

## Shiny App Introduction

My app was designed to do the following
- Display the trend of `pressure` over time across many storm states
- Show a linear regression model for each state
- Add controls to adjust which storm states are shown in the plot
- Storm states
```{r}
storms$status |> unique()  
```

## Final Remarks

Thank you for reading and checking out my first app!